Multi-Resolution Spatiotemporal Neural Field Estimation

### 2011-03-09 Multiresolution_framework/ltx/manuscript.tex
minor edits
minor change to fig2

\author{P. Aram, D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M. Dewar, K.Scerri~\IEEEmembership{Member,~IEEE,}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta.}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

@@

\begin{abstract}
%\boldmath
The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
% Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
% \end{IEEEkeywords}
% \IEEEpeerreviewmaketitle
\section{Introduction}
\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons. This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics. This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.

>>>>

\author{P. Aram, D.R. Freestone~\IEEEmembership{Graduate Student Member,~IEEE}, M. Dewar, K.Scerri~\IEEEmembership{Member,~IEEE}, D.B. Grayden~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia. The Bionic Ear Institute acknowledges the support it receives from the Victorian State Government through the Operational Infrastructure Support Program.}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta.}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

@@

\begin{abstract}
%\boldmath
The Integro-difference equation (IDE) is an increasingly popular model of spatio-temporal processes. Here we develop a multi-resolution approximation (MRA) framework for the IDE neural field equations based on semi-orthogonal cardinal B-spline wavelets. State and parameter estimation is performed using the Expectation Maximization (EM) algorithm. A synthetic example is provided
to demonstrate the framework.
\end{abstract}
% Note that keywords are not normally used for peerreview papers.
% \begin{IEEEkeywords}
%  Neural field model, multiresolution approximation (MRA), Expectation Maximization (EM) algorithm, wavelets.
%  \end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
\ifCLASSOPTIONpeerreview
  \begin{center} \bfseries EDICS Category: SSP-IDEN \end{center}
  \fi
%
%  For peerreview papers, this IEEEtran command inserts a page break and
%creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
\IEEEPARstart{T}{he} human cerebral cortex has a multi-resolution architecture, where spatial scales for information processing range from ion channels, to single neurons, to networks of millions of neurons. This multi-resolution cortical architecture poses major modeling challenges to efficiently describe the brain's dynamics. This paper introduces a multi-resolution data-driven framework for neural field modeling, the Multi-Resolution Approximate Integro-Difference Equation (MRAIDE), to address this challenge.
